---
title: "Visualizing data with ggplot2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load R Studio Packages and Datasets

This code was taken from an [example](www.kaggle.com/rtatman/visualizing-data-with-ggplot2#Table-of-Contents) by Rachael Tatman in Kaggle.
 ^[TATMAN, RACHAEL. “Visualizing Data with GGPLOT2.” Kaggle, Kaggle, 9 Jan. 2018, www.kaggle.com/rtatman/visualizing-data-with-ggplot2#Table-of-Contents. ]
 
 

```{r cars}
# read in our libraries
library(tidyverse) # includes ggplot2
library(ggthemes) # includes pre-made themes we'll use near the end
library(readr)

# read in our data
candyRankings <- read_csv("candy-data.csv")
candyProduction <- read_csv("candy_production.csv")

```

## Plot Data

```{r pressure, echo=FALSE}
# first we need to set up our plot
ggplot(data = candyRankings, aes(x = sugarpercent, 
                                 y = pricepercent, 
                                 label = competitorname
                                )) +
    geom_smooth(method = "lm") + # and then add a fitted line
    geom_text(check_overlap = T,# automatically reduce overlap (deletes some labels)
              angle = 30,# tilt the text 30 degrees
              size = 2.5 # make the text smaller (to reduce overlap more)
             ) + # and then add labels to the points
    labs(title = "More sugary candies are more expensive", # plot title
         x = "Sugar content (percentile)", # x axis label
         y = "Price (percentile)" # y axis label
        )
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

**Citations**




